A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
V.B

\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\summary}[1]{({\csname #1Min\endcsname} / {\csname #1Mean\endcsname} / {\csname #1Max\endcsname})}

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has \summary{CorpusRevdeps}
reverse dependencies (min / mean / max) and consists of \CorpusRCodeRnd lines of
R code and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran).
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means. Large
(over \CorpusLargePackageTresholdRnd lines of code) and popular (in
\CorpusMostDownloadedTreshold most downloaded) packages are annotated.

These packages come from the Comprehensive R Archive Network
(CRAN\footnote{\url{http://cran.r-project.org}}), the largest repository of R
code with over \CorpusAllCranRnd packages\footnote{CRAN receives about 6 new
  package submissions a day~\cite{Ligges2017}}. Unlike other open code
repositories such as GitHub, CRAN is a curated repository. Each submitted
package must abide to a number of well-formedness rules that are automatically
checked asserting certain quality. Most relevant for this work is that all of
the \emph{runnable code} is tested and only a successfully running package is
admitted in the archive. This is important as we use this runnable code for the
dynamic analysis of eval calls.

@@

\subsection{Kaggle sripts}
% contrast to CRAN - duplication

>>>>

\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\summary}[1]{({\csname #1Min\endcsname} / {\csname #1Mean\endcsname} / {\csname #1Max\endcsname})}
\newcommand{\summaryrnd}[1]{({\csname #1MinRnd\endcsname} / {\csname #1MeanRnd\endcsname} / {\csname #1MaxRnd\endcsname})}

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and
should have better code coverage. The resulting set has \summary{CorpusRevdeps}
reverse dependencies (min / mean / max) and consists of \CorpusRCodeRnd lines of
R code and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran).
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

All included packages come from the Comprehensive R Archive Network
(CRAN\footnote{\url{http://cran.r-project.org}}), the largest repository of R
code with over \CorpusAllCranRnd packages\footnote{CRAN receives about 6 new
  package submissions a day~\cite{Ligges2017}}. Unlike other open code
repositories such as GitHub, CRAN is a curated repository. Each submitted
package must abide to a number of well-formedness rules that are automatically
checked asserting certain quality. Most relevant for this work is that all of
the \emph{runnable code} is tested and only a successfully running package is
admitted in the archive. This is important as we use this runnable code for the
dynamic analysis of eval calls.

@@

\subsection{Kaggle Scripts}

To represent user-written code in the corpus, we truned to
Kaggle\footnote{\url{https://www.kaggle.com}}, an online platform for
data-science and machine-learning practitioner. Among others, the website allow
people to share data-science competitions, a data-analysis problem together with
data, for which users try to find the best solution. The solutions, called
\emph{kernels}, are then shared back to the platform in the form of either plain
scripts or as Rmarkdown / Jupyter notebooks written in either Julia, Python, R
or SQLite.

One of the most popular competition is about predicting passenger survival on
Titanic\footnote{\url{https://www.kaggle.com/c/titanic}} with \CorpusKaggle
kernels in R (over 1/4 of all available R kernels) which we used for our corpus.

Unlike CRAN, Kaggle is not a curated repository and therefore there are no
guarantees about the quality of the code. After downloading all of the
\CorpusKaggle kernels and extracting the R code from the various
formats\footnote{We use \texttt{rmarkdown} package to convert from Jupyer
  notebook to Rmarkdown as well as to convert from Rmarkdown to plain R}, we
found that \CorpusDuplicatedKaggle were whole-file duplicates. From
\CorpusRunnableKaggle kernels, \CorpusFailedKaggle failed to execute. Next to
various runtime exceptions, common problems were parse errors and misspelled
package names.

The final set contains \CorpusFinishedKaggle kernels with
\CorpusFinishedKaggleCodeRnd \summaryrnd{CorpusFinishedKaggleCode} lines of R
code.
